Codebook
========
Generated on `r as.character(Sys.time())` during the same process that generated 'tidy_data.txt'.

Variable list and descriptions
------------------------------

Variable name    | Description
-----------------|------------
featureCode      | Code of feature for easy lookup in 'features.txt'
subject          | ID the subject who performed the activity for each window sample. Its range is from 1 to 30.
activityNum      | Number corresponding to activity. Ranges from 1 to 6.
activityName     | Name of the activity. Factor with 6 levels.
value            | Value which is the combination of train- and testdata
featureNum       | Number corresponding to feature in 'features.txt'
featureName      | Names of features as given in 'features.txt'

Datatable structure
-----------------

```{r}
str(dt)
```


Show a few rows of the dataset
------------------------------

```{r}
head(dt)
tail(dt)
```

Summary of variables
--------------------

```{r}
summary(dt)
```

Save to file
------------

Save data table objects to a tab-delimited text file called `"tidy_data.txt"`.

```{r save}
write.table(tidyData, "tidy_data.txt", row.names = FALSE, quote = FALSE,col.names = TRUE, sep="\t")

```